Dirichlet discretization of Neumann problems

### 2020-01-06 paper_lap/06num.tex
changes

\section{Numerical results}
\subsection{Accuracy}
In this section, we demonstrate accuracy of the proposed numerical method (both in the "weak" sense, and 
"strong sense" after sufficiently many re-solves) on the triangular domain shown below. 
The reference solution for each of the examples is computed using a discretization with
a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-150}$ times
the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). 
\begin{rem}
$2^{-150}$ is significantly smaller than machine precision, however the matrix entries corresponding to the
corner interactions can be computed accurately by recentering the corner at the origin. 
\end{rem} 
\begin{rem}
It is well-known that a smallest panel size of $2^{-100}$ is sufficient to resolve the density corresponding
to solutions of the Neumann problem in order to obtain full machine precision in the solution anywhere in the volume.
However, it is not true the value of the density is accurate to machine precision at all the nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$. 
\end{rem}
In these examples, the solutions are computed dense linear solves.

>>>>

\section{Numerical results}
\subsection{Accuracy}
In this section, we demonstrate the accuracy of the proposed numerical method (both in the {\it weak} sense 
described above, 
as well as in the classical sense after sufficiently many re-solves) on the triangular domain shown below. 
The reference solution for each of the examples is computed using a discretization with
a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-150}$ times
the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). 
\begin{rem}
Though $2^{-150}$ is significantly smaller than machine precision, the matrix entries corresponding to the
corner interactions can be computed accurately by {\color{red}translating the corners to the origin when 
computing interactions of nearby points.} 
\end{rem} 
\begin{rem}
Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
machine precision 
($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel size (i.e. the size of the 
panel closest to the corner) to be of size $2^{-100}.$ However, it is not true that the value of the density is 
accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$.

It is well-known that a smallest panel size of $2^{-100}$ is sufficient to resolve the density corresponding
to solutions of the Neumann problem in order to obtain full machine precision {\color{red}($\sim 1.11 \times 10^{-16}$)} for the solution anywhere in the volume {\color{red} sufficiently far from the corner.}
However, it is not true that the value of the density is accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$. 
\end{rem}
In these examples, the solutions are computed dense linear solves.
